%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     File: ExtendedAbstract_abstr.tex                               %
%     Tex Master: ExtendedAbstract.tex                               %
%                                                                    %
%     Author: Andre Calado Marta                                     %
%     Last modified : 2 Dez 2011                                     %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% The abstract of should have less than 500 words.
% The keywords should be typed here (three to five keywords).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%
%% Abstract
%%
\begin{abstract}

Children that have problems in developing socialization before his teens can become socially isolated, leading to low self-esteem and social alienation, and possibly snowballing into more serious psychological problems further into adulthood. In this document we present a proposal and implementation for a Serious Game, LINA, that uses Contact Theory to help pre-adolescent children improving the relations with their peers. In LINA, the players, children from 10 to 12 years old, will try to find out what happened to a missing colleague - Lina - and her story through the discovery of augmented reality clues and overcoming challenges cooperatively. This document specifies the game concept, methodology and implementation of a digital prototype for demonstration. Also evaluates said prototype regarding its usability, enjoyment and interest for the players. Conducted evaluation determined that the players find the gameplay and story fun and are keen on playing more of the game. Future work involves revising this first prototype with the feedback from the evaluation session, coming up with new challenges and exploring technical limitations of Augmented Reality in the game context.

%%
%% Keywords (max 5)
%%
\noindent{{\bf Keywords:}} Augmented Reality; Contact Theory; Serious Game; User-Centered Design.
\end{abstract}

